\LARGE \bf Approximately Orchestrated Routing and Transportation Analyzer:\\ Large-scale Traffic Simulation for Autonomous Vehicles

### 2012-03-15 papers/itsc_2012/final.tex
edits to results

\subsection{Intersection Policies}

@@

The experiment simulates a 9$\times$11km$^{2}$ slice of downtown Austin,
Texas\footnote{bounded by the Mopac and Springdale Road horizontally, and Oltorf
Street and Koenig Lane vertically}, and a 15$\times$13km$^{2}$ slice of downtown
Houston, Texas \footnote{bounded by Ella Boulevard and Eastex Freeway
horizontally, and West Alabama Street and Crosstimbers Street vertically}, for
one hour. The step duration is fixed at 0.1 seconds. While the intersection
policies vary, the agents spawned and their routes remain the same.  A generator
creates one new agent every 1 simulation second, with a uniformly random
starting position and goal.

@@

If an agent travels along a lane at the speed limit and does not slow down to
wait at an intersection, then it traverses the lane in an optimal amount of
time. If the intersection orders it to stop or if other agents in the same lane
have slowed down by the intersection's orders, then the intersection has caused
some delay. This delay can be used as one measure of intersection performance.
Figures \ref{fig:avg_lag_atx} and \ref{fig:avg_lag_houston} graph the average of
this delay per agent. On average, reservation policies cause less than 1 second
of delay at each intersection, stop signs cause about 7 seconds lag, and traffic
signals using the heuristic described above cause 16 seconds. These results will
vary with different traffic levels and policy configurations, so the important
demonstration is that AORTA can be used as a framework for evaluating these
policies.

The number of agents driving at some time changes because the continuous
generator introduces a new agent every second. This count reaches a steady
state when the generator introduces an agent at the same rate as older agents
finish their route. Figure \ref{fig:agent_cnt} reveals that autonomous
reservations let agents reach their destination twice as quickly as the
competition, with a steady-state of about 400 agents. The count for traffic
signals continues to increase because gridlock occurred in one segment of the
map, causing agents to not finish their route.  Unexpected starvation was also
observed: although the signals cycle through turns regularly, agents cannot
proceed when the previous cycle caused a destination lane to fill and become
blocked.

Users could conduct this experiment and many others without needing to
understand most of AORTA's code-base. The largest intersection policy, traffic
signals with the flooding heuristic for timing assignment, is only 400 lines of
code in Scala.

>>>>

\subsection{Intersection Policies}
\label{sec:policies}

@@

The experiment simulates one hour of traffic in two cities: a
9$\times$11km$^{2}$ slice of downtown Austin, Texas\footnote{bounded by the
Mopac and Springdale Road horizontally, and Oltorf Street and Koenig Lane
vertically}, and a 15$\times$13km$^{2}$ slice of downtown Houston, Texas
\footnote{bounded by Ella Boulevard and Eastex Freeway horizontally, and West
Alabama Street and Crosstimbers Street vertically}.  The step duration is fixed
at 0.1 seconds. While the intersection policies vary, the agents spawned and
their routes remain the same.  A generator creates one new agent every 1
simulation second, with a uniformly random starting position and goal.

@@

If an agent travels along a lane at the speed limit and does not slow down to
wait at an intersection, then it traverses the lane in an optimal amount of
time. If the intersection orders it to stop or if other agents in the same lane
have slowed down by the intersection's orders, then the intersection has caused
some delay. This delay can be used as one measure of intersection performance.
Figures \ref{fig:avg_lag_atx} and \ref{fig:avg_lag_houston} graph the average of
this delay per agent. Similar trends are observed in both cities: an average of
less than 1 second of delay at autonomous reservation intersections, 7 (Austin)
or 8 (Houston) seconds at stop signs, and 16 (Austin) or 17 (Houston) seconds at
traffic signals using the heuristic described above.  These results will vary
with different traffic levels and policy configurations, so the important
demonstration is that AORTA can be used as a framework for evaluating these
policies.

The number of agents driving at some time changes because the continuous
generator introduces a new agent every second. This count reaches a steady state
when the generator introduces an agent at the same rate as older agents finish
their route. Figure \ref{fig:agent_cnt_atx} reveals that autonomous reservations
let agents reach their destination twice as quickly as the competition in
Austin, with a steady-state of about 400 agents. There, the count for traffic
signals continues to increase because gridlock occurred in one segment of the
map, causing agents to not finish their route. Figure
\ref{fig:agent_cnt_houston} revals a similar trend in Houston, except that
gridlock occurred both during the trial with traffic signals and stop signs.
Unexpected starvation was also observed: although the signals cycle through
turns regularly, agents cannot proceed when the previous cycle caused a
destination lane to fill and become blocked.

Repeating this or other experiments in more locations only requires those
locations to be exported from the OSM website. Editing the intersection policies
is similarly convenient, as users can ignore most of AORTA's code-base and just
change the logic described in section \ref{sec:policies}.  For reference, the
most complex intersection policy, traffic signals with the flooding heuristic
for timing assignment, is only 400 lines of code in Scala.
